Tropical Andes plant trait data GIFT

### 2023-10-18 code/L0/L0_TropicalAndes_plants_GIFT.Rmd
standardizing code file naming
remove species list, add more traits

# Load in species list
```{r}
species_list <- read.csv("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1/TropicalAndes_plant_Forest_SpeciesList.csv")
species_list <- species_list$x
```

# Retrive GIFT data
```{r}
trait_meta <- GIFT_traits_meta()
```
Traits of interest: plant height (ID = 1.6.3), lifespan (ID = 2.2.1), dispersal syndrome (ID = 3.3)

```{r}
# 
height <- GIFT_traits(trait_IDs = c("1.6.2"))
lifespan <- GIFT_traits(trait_IDs = c("2.2.1"))
dispersal_syndrome <- GIFT_traits(trait_IDs = c("3.3.1", "3.3.2"))
```

@@

>>>>

# Retrive GIFT data
```{r}
trait_meta <- GIFT_traits_meta()
```
Traits of interest: plant height (ID = 1.6.3), lifespan (ID = 2.2.1), dispersal syndrome (ID = 3.3), Plant_height_min (1.6.1), Plant_height_max (1.6.2), Fruit_type_1 (3.16.1), fruit_dryness_1 (3.18.1), Fruit_length_min (3.13.1), Fruit_length_max (3.13.2), Fruit_length_mean (3.13.3), Seed_mass_min (3.2.1), Seed_mass_max (3.2.2), Seed_mass_mean (3.2.3), Seed_length_min (3.10.1), Seed_length_max (3.10.2), Seed_length_mean (3.10.3), Seed_width_min (3.11.1), Seed_width_max (3.11.2), Seed_width_mean (3.11.3)

```{r}
# 
height <- GIFT_traits(trait_IDs = c("1.6.2", "1.6.1", "1.6.3"))
lifespan <- GIFT_traits(trait_IDs = c("2.2.1"))
dispersal_syndrome <- GIFT_traits(trait_IDs = c("3.3.1", "3.3.2"))
fruit_type <- GIFT_traits(trait_IDs = c("3.16.1", "3.18.1"))
fruit_length <- GIFT_traits(trait_IDs = c("3.13.1", "3.13.2", "3.13.3"))
seed_mass <- GIFT_traits(trait_IDs = c("3.2.1", "3.2.2", "3.2.3"))
seed_length <- GIFT_traits(trait_IDs = c("3.10.1", "3.10.2", "3.10.3"))
seed_width <- GIFT_traits(trait_IDs = c("3.11.1", "3.11.2", "3.11.3"))
```

@@

```{r}
GIFT_traits %>% count(trait_name)
```
